A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-30 latex/paper.tex
reword

Overall, our experiments did not show any substantial performance
difference between Spark and Dask. In contradiction with the experiments
of~\cite{Mehta:17}, we did not observe consequential overhead differences
due to serialization or startup costs. This apparent contradiction is most
likely coming from differences in applications: while the applications in
~\cite{Mehta:17} were mostly compute-intensive, ours were more data-intensive.
Consequently, in our case, potential
overhead differences were compensated by reverse trends in data transfer
time. Since our focus are Big Data applications, this leads us to conclude that 
engines are equivalent. However, this conclusion doesn't invalidate the results of~\cite{Mehta:17} that 
would apply to more compute-intensive applications.

>>>>

Overall, our experiments did not show any substantial performance
difference between Spark and Dask. In contradiction with the experiments
of~\cite{Mehta:17}, we did not observe consequential overhead differences
due to serialization or startup costs. This apparent contradiction is most
likely coming from differences in applications, engine parametrizations, or
infrastructure characteristics. In our case, potential overhead differences were
compensated by reverse trends in data transfer time. Since our focus are
Big Data applications, this leads us to conclude that engines are
equivalent.
